More equivalences for Open pNets\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2017-10-16 2016-Weak-FH-Bisim/WeakBisim.tex
Solved some comments

%\smallskip\noindent
\paragraph*{Notations.}
We extensively use indexed structures
over some countable indexed sets, which are equivalent to mappings over
the countable set. % . The indexes will usually be
% integers, bounded or not. Such an indexed family is
%denoted
%follows:
$a_i^{i\in I}$
%, or equivalently  $(i\mapsto a_i)^{i\in I}$
denotes a family of elements $a_i$ indexed over the
set $I$. % Such a family
% is equivalent to the mapping $(i\mapsto a_i)^{i\in I}$.
% To specify the set over which the structure is indexed,
% indexed structures are always denoted with an exponent of the form $i\in I$
% (arithmetic only appears in the indexes if necessary).
$a_i^{i\in I}$ defines both $I$ the set over which the family is
indexed (called \emph{range}), and $a_i$ the elements of the family.
E.g., $a^{i\in\{3\}}$ is the mapping with a single entry $a$ at index
$3$ ; abbreviated $(3\mapsto a)$ in the following.
When this is not
ambiguous, we shall use notations for sets, and typically write
``indexed set over I'' when formally we should speak of multisets, and
write $x\in a_i^{i\in I}$ to mean $\exists i\in I.\, x=a_i$.  An empty
family is denoted $\emptyset$. We
denote classically $\overline{a}$ a family when the indexing set is
not meaningful.  $\uplus$ is the disjoint union on
indexed sets.

@@

\RAB{La notation overline n'a pas ete introduite auparavant? Aussi, je n'ai pas trop bien saisi quand on utilise overline et la la notation k in K}

@@

\TODO{say that This predicate entails a verification of satisfiability}

@@

The equivalence we need is a strong bisimulation between
pNets having exactly the same Holes with the same sorts, but using a
flexible matching 
between open transition, to accommodate comparisons between pNet
expressions with different architectures.
 We name it FH-bisimulation,
 as a short cut for the ``Formal Hypotheses'' manipulated in the
 transitions, but also as a reference to the work of De Simone~\cite{deSimone85},
 that pioneered this idea.\\
\TODO{To check:}
Let \ERIC{$\mathcal{R}=\{(s^1,s^2|\Pred_{s^1,s^2})\}$} be a relation over the set $\mathcal{S}_1$ and $\mathcal{S}_2$ constrained by a predicate
More precisely, for any pair $(s^1,s^2)$, there is a 
   single
      $(s^1,s^2|\Pred_{s^1,s^2})\in\mathcal{R}$  stating that $s^1$ and $s^2$ are related if $\Pred_{s^1,s^2}$\ 
      is 
      true.

\RAB{ I propose:
Let $\mathcal{R}=\{(s^1,s^2|\Pred_{s^1,s^2})\}$ be a relation over the set $\mathcal{S}_1$ and $\mathcal{S}_2$ constrained by a predicate: if $(s^1,s^2) \in \mathcal{R}$ then $\Pred_{s^1,s^2}$ is  true.}

@@

\noindent
\begin{minipage}{0.69\linewidth} 	Suppose that
   $A_1 = <L_1,J,\mathcal{S}_1, s^1_0,
   \mathcal{T}_1>$ and $A_2 = <L_2,J,\mathcal{S}_2,s^2_0, \mathcal{T}_2>$
   are open automata where the set
   of holes are equal %\LUDO{added:} 
   and of the same sort.  %\LUDO{changed:} 
\end{minipage}
\hspace{2mm}
\begin{minipage}{0.30\linewidth}
	\includegraphics[width=\linewidth]{XFIG/Bisim}
\end{minipage}
 Then 
   $\mathcal{R}$ is an FH-bisimulation iff for any  states
   $s^1\in\mathcal{S}_1$ and\\ $s^2\in\mathcal{S}_2$, $(s^1,s^2|\Pred)\in\mathcal{R}$, we 
   have
   the following:

>>>>

%\smallskip\noindent
\paragraph*{Notations.}
We extensively use indexed structures
over some countable indexed sets, which are equivalent to mappings over
the countable set. % . The indexes will usually be
% integers, bounded or not. Such an indexed family is
%denoted
%follows:
$a_i^{i\in I}$
%, or equivalently  $(i\mapsto a_i)^{i\in I}$
denotes a family of elements $a_i$ indexed over the
set $I$. % Such a family
% is equivalent to the mapping $(i\mapsto a_i)^{i\in I}$.
% To specify the set over which the structure is indexed,
% indexed structures are always denoted with an exponent of the form $i\in I$
% (arithmetic only appears in the indexes if necessary).
$a_i^{i\in I}$ defines both $I$ the set over which the family is
indexed (called \emph{range}), and $a_i$ the elements of the family.
E.g., $a^{i\in\{3\}}$ is the mapping with a single entry $a$ at index
$3$ ; abbreviated $(3\mapsto a)$ in the following.
When this is not
ambiguous, we shall use notations for sets, and typically write
``indexed set over I'' when formally we should speak of multisets, and
write $x\in a_i^{i\in I}$ to mean $\exists i\in I.\, x=a_i$.  An empty
family is denoted $\emptyset$. We
denote classically with an overline -- $\overline{a}$  -- a family when the indexing set 
is
not meaningful.  $\uplus$ is the disjoint union on
indexed sets.

@@

\RAB{La notation overline n'a pas ete introduite auparavant? Aussi, je n'ai pas trop bien 
saisi quand on utilise overline et la la notation k in K}\LUDO{DONE}

@@

Somehow, this predicate entails a verification of satisfiability in the sense that if the 
predicate $\Pred_{\symb{sv}}$ is not satisfiable, then the transition associated with the 
synchronisation will not occur in the considered state.

@@

The equivalence we need is a strong bisimulation between
pNets having exactly the same Holes with the same sorts, but using a
flexible matching 
between open transition, to accommodate comparisons between pNet
expressions with different architectures.
 We name it FH-bisimulation,
 as a short cut for the ``Formal Hypotheses'' manipulated in the
 transitions, but also as a reference to the work of De Simone~\cite{deSimone85},
 that pioneered this idea.\\
\TODO{To check:}
Let \ERIC{$\mathcal{R}=\{(s^1,s^2|\Pred_{s^1,s^2})\}$} be a relation over the set $\mathcal{S}_1$ and $\mathcal{S}_2$ constrained by a predicate
More precisely, for any pair $(s^1,s^2)$, there is a 
   single
      $(s^1,s^2|\Pred_{s^1,s^2})\in\mathcal{R}$  stating that $s^1$ and $s^2$ are related 
      if $\Pred_{s^1,s^2}$ 
      is 
      true, i.e. the states are related when the variables in $s^1$ and $s^2$ verify the 
      predicate $\Pred_{s^1,s^2}$.

\RAB{ I propose:
Let $\mathcal{R}=\{(s^1,s^2|\Pred_{s^1,s^2})\}$ be a relation over the set 
$\mathcal{S}_1$ and $\mathcal{S}_2$ constrained by a predicate: if $(s^1,s^2) \in 
\mathcal{R}$ then $\Pred_{s^1,s^2}$ is  true.}  \LUDO{No : this is not the meaning}

@@

\noindent
\begin{minipage}{0.69\linewidth} 	Suppose that
   $A_1 = <L_1,J,\mathcal{S}_1, s^1_0,
   \mathcal{T}_1>$ and $A_2 = <L_2,J,\mathcal{S}_2,s^2_0, \mathcal{T}_2>$
   are open automata where the set
   of holes are equal %\LUDO{added:} 
   and of the same sort.  %\LUDO{changed:}

 Then 
$\mathcal{R}$ is an FH-bisimulation iff for any  states
$s^1\in\mathcal{S}_1$ and $s^2\in\mathcal{S}_2$, $(s^1,s^2|\Pred)\in\mathcal{R}$, we 
have
the following:
\end{minipage}
\hspace{2mm}
\begin{minipage}{0.30\linewidth}
	\includegraphics[width=\linewidth]{XFIG/Bisim}
\end{minipage}
